---
title: "eds 221 day 4 session 1"
format: html
editor: visual
---

```{r}
library(tidyverse)
```

## Functions

make a function that doubles a value

```{r}
double_value <- function(my_dollars) {
  print(2 * my_dollars)
}
```

```{r}
double_value(10.13)
```

```{r}
monthly_income <- c(42.50, 50.54 )


```

create a function that returns an awesome restaurant name given a cool animal and your favorite food

```{r}
name_restaurant <- function(animal, food) {
  print(paste0(animal, food))
}
name_restaurant('rats', 'spaghetti')
```

```{r}
# given temperature in degrees farenheit white a function that converts it to celsius
```

```{r}
convert_celsius <- function(degrees){
  print((degrees - 32) * (5/9))
}

convert_celsius(52)

```

create a function that given inputs of age and hometown, returns 'i am \_\_ years old, and im from \_\_\_'

```{r}
info_me <- function(age, hometown) {
  print(paste('i am', age, 'years old and im from', hometown))
}

info_me(22, 'port hueneme')
```

```{r}
calculate_animal_years <- function(species, age_human_years) {   if (species == 'dog') {     age_human_years *7   } else if (species == 'goat') {     age_human_years * 4.7   } else {     print('please enter dog or goat')   } }  calculate_animal_years('dog', 10)
```

write a function that, given temperature in kelvin, if a user selects 'metric' to the scale, then return degrees celsius, or if they select 'english, then return degrees in fahrenheit

```{r}
temperature <- function(scale, degrees) {   if (scale == 'metric') {     degrees - 273.15   } else if (scale == 'english') {     (degrees - 273.15) * 1.8 + 32   } else {     print('please use english or metric scale')   } }  temperature('metric', 300)
```

°F = (K − 273.15) × 1.8 + 32

## More Functions

we are gonna create a data frame, and our fucntion is going to output a row of out data?

create a subset within a function, and return something based on that subset

```{r}
dog_choice <- data.frame(dog_name = c('khora', 'teddy', 'waffle', 'banjo', 'tallie'),
                         food = c('everything', 'salmon', 'pancakes', 'chicken', 'enchiladas'))
```

```{r}
dog_menu <- function(enter_dog_name) {
  my_subset <- filter(dog_choice, dog_name == enter_dog_name)
   print(paste('my name is', my_subset$dog_name, 'and my favorite food is', my_subset$food))
}
```

```{r}
dog_menu('concha')
```

## Function with a for loop

```{r}
df_means <- function(df) {
  for (i in seq_along(df)) {
    col_mean <- mean(df[[i]], na.rm = TRUE, 2)
    column_name <- colnames(df[i])
    print(paste('the mean value of', column_name, 'is', col_mean))
  }
}
```

```{r}
df_means(mtcars)
```

```{r}
df_means(faithful)
```
<<<<<<< HEAD

git
=======
>>>>>>> fd359d6d850f91e087fe3bc40e7f5e4c05325515
