---
title: "eds 221 day 4 session 1"
format: html
editor: visual
---

## Functions

make a function that doubles a value

```{r}
double_value <- function(my_dollars) {
  print(2 * my_dollars)
}
```

```{r}
double_value(10.13)
```

```{r}
monthly_income <- c(42.50, 50.54 )


```

create a function that returns an awesome restaurant name given a cool animal and your favorite food

```{r}
name_restaurant <- function(animal, food) {
  print(paste0(animal, food))
}
name_restaurant('rats', 'spaghetti')
```

```{r}
# given temperature in degrees farenheit white a function that converts it to celsius
```

```{r}
convert_celsius <- function(degrees){
  print((degrees - 32) * (5/9))
}

convert_celsius(52)

```

create a function that given inputs of age and hometown, returns 'i am \_\_ years old, and im from \_\_\_'

```{r}
info_me <- function(age, hometown) {
  print(paste('i am', age, 'years old and im from', hometown))
}

info_me(22, 'port hueneme')
```

```{r}
calculate_animal_years <- function(species, age_human_years) {
  if (species == 'dog') {
    age_human_years *7
  } else if (species == 'goat') {
    age_human_years * 4.7
  } else {
    print('please enter dog or goat')
  }
}

calculate_animal_years('dog', 10)
```

write a function that, given temperature in kelvin, if a user selects 'metric' to the scale, then return degrees celsius, or if they select 'english, then return degrees in fahrenheit

```{r}
temperature <- function(scale, degrees) {
  if (scale == 'metric') {
    degrees - 273.15
  } else if (scale == 'english') {
    (degrees - 273.15) * 1.8 + 32
  } else {
    print('please use english or metric scale')
  }
}

temperature('metric', 300)
```

°F = (K − 273.15) × 1.8 + 32
